Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-22 paper.tex
rm todo
reply

@@

This section presents our first contribution, the definition of
hypercoercions.  The design of hypercoercions is motivated by the
observation that a normal coercion has at most three parts;
projections are always at the beginning; injections and failures are
always at the end. Hypercoercions make this structure explicit: a
hypercion either is $\hyperCoercionI$, the identity cast for
$\TOOdyn$, or contains three parts, where the first part is either a
projection or the identity and the last part is either an injection, a
failure, or the identity.

\todo[inline]{What about the middlepart? -JS}

@@

\todo[inline]{KC, please add the definition of $L$ -JS}

>>>>

% LCast
\newcommand{\lsOOcast}[3]{\cOOcast{#1}{#2}{#3}}
\newcommand{\lcOOnull}[0]{[]}
\newcommand{\lcOOcons}[2]{#1 \; :: \; #2}

@@

This section presents our first contribution, the definition of
hypercoercions.  The design of hypercoercions is motivated by the
observation that a normal coercion has at most three parts;
projections are always at the beginning; injections and failures are
always at the end. Hypercoercions make this structure explicit: a
hypercion either is $\hyperCoercionI$, the identity cast for
$\TOOdyn$, or contains three parts, where the first part is either a
projection or the identity, the last part is either an injection, a
failure, or the identity, and each kind of middle part corresponds to a type 
constructor and include hypercoercion(s) for subpart(s) of corresponding values.
\todo[inline]{What about the middlepart? -JS
\\---\\
Fixed. -KC}

@@

\begin{figure}
Syntax
\[
\begin{array}{rclr}
\stxrule{c}{casts}{\lcOOnull{} \mid \lcOOcons{s}{c}}
\stxrule{s}{steps}{\lsOOcast{T}{l}{T}}
\end{array}
\]

Steps Typing
\fbox{$\judgeTypeFT{s}{T}{T}$}
\begin{gather*}
\inference{
	T_1 \neq T_2
}{
	\judgeTypeFT{\lsOOcast{T_1}{l}{T_2}}{T_1}{T_2}
}
\end{gather*}

Casts typing
\fbox{$\judgeTypeFT{c}{T}{T}$}
\begin{gather*}
\inference{
}{
	\judgeTypeFT{\lcOOnull}{T}{T}
}
\quad
\inference{
	\judgeTypeFT{s}{T_1}{T_2} &
	\judgeTypeFT{c}{T_2}{T_3}
}{
	\judgeTypeFT{\lcOOcons{s}{c}}{T_1}{T_3}
}
\end{gather*}

\fbox{$seq(c,c)=c$}
\[
\begin{array}{rclr}
\funrule{seq(\lcOOnull,c)}{c}{}
\funrule{seq(\lcOOcons{s}{c'},c)}{\lcOOcons{s}{seq(c',c)}}{}
\end{array}
\]

\fbox{$id(T)=c$}
\[
\begin{array}{rclr}
\funrule{id(T)}{\lcOOnull}{}
\end{array}
\]

\fbox{$cast(T,l,T)$}
\[
\begin{array}{rclc}
\funrule{cast(T_1,l,T_2)}{
	\lcOOnull
}{
	\sidecond{T_1 = T_2}
}
\funrule{cast(T_1,l,T_2)}{
	\lcOOcons{\lsOOcast{T_1}{l}{T_2}}{\lcOOnull}
}{
	\sidecond{T_1 \neq T_2}
}
\end{array}
\]

\fbox{$appS(v,s) = r$}
\[
\begin{array}{rclr}
\funrule{
	appS(v,\cOOcast{\star}{l}{\star})
}{
	\rOOsucc{v}
}{}
\funrule{
	appS(\vOOcast{v}{\cOOcast{P_1}{l_1}{\star}},\cOOcast{\star}{l_2}{P_2})
}{
	\rOOsucc{v}
}{\sidecond{P_1 = P_2}}
\funrule{
appS(\vOOcast{v}{\cOOcast{P_1}{l_1}{\star}},\cOOcast{\star}{l_2}{P_2})
}{
appS(v,\cOOcast{P_1}{l_2}{P_2})
}{\sidecond{P_1 \neq P_2}}
\funrule{
	appS(v,\cOOcast{P}{l}{\star})
}{
	\rOOsucc{\hcvOOinj{P}{v}}
}{}
\funrule{
	appS(v,\lsOOcast{\POOunit}{l}{\POOunit})
}{
	\rOOsucc{v}
}{}
\funrule{
	appS(
		\hcvOOfun{c_1}{\rho}{x}{e}{c_2},
		\lsOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}})
}{
	\rOOsucc{(\hcvOOfun{c_1'}{\rho}{x}{b}{c_2'})}
}{
	\\ &&
	\text{where} \;
	c_1' = seq(cast(T_3,l,T_1),c_1)
	\\ &&
	\text{and} \;
	c_2' = seq(c_2,cast(T_2,l,T_4))
}

\funrule{
	appS(
		\hcvOOcons{v_1}{c_1}{v_2}{c_2},
		\lsOOcast{\POOprod{T_1}{T_2}}{l}{\POOprod{T_3}{T_4}}
}{
	\rOOsucc{(\hcvOOcons{v_1}{c_1'}{v_2}{c_2'})}
}{
\\ &&
\text{where} \;
c_1' = seq(c_1,cast(T_1,l,T_3))
\\ &&
\text{and} \;
c_2' = seq(c_2,cast(T_2,l,T_4))
}
\funrule{
	appS(\hcvOOinl{v}{c},\lsOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}})
}{
	\rOOsucc{(\hcvOOinl{v}{seq(c,cast(T_1,l,T_3))})}
}{}
\funrule{
	appS(\hcvOOinr{v}{c},\lsOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}})
}{
	\rOOsucc{(\hcvOOinr{v}{seq(c,cast(T_2,l,T_4))})}
}{}
\funrule{
	appS(v,\cOOcast{P_1}{l}{P_2})
}{
	\rOOfail{l}
}{\sidecond{\neg P_1 \smile P_2}}

\end{array}
\]

\fbox{$applyCast(v,c) = r$}
\[
\begin{array}{rclr}
\funrule{
	applyCast(v,\lcOOnull)
}{
	\rOOsucc{v}
}{}
\funrule{
	applyCast(v,\lcOOcons{s}{c})
}{
	applyStep(v,s) >>= \lambda v. applyCast(v,c)
}{}
\end{array}
\]

	\caption{The $L$ Lazy D Cast ADT}
\end{figure}
